---
title: "Youtube Music Channels Analysis"
author: "Harshad Jadhav"
date: "29/01/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem Statement






## Installing and importing required packages
```{r}
#install.packages("tidyverse")
#install.packages("ggplot2")
#install.packages("ggthemes")
#install.packages("cowplot")
#install.packages("lubridate")
#install.packages("forcats")

library(tidyverse)
library(ggthemes)
library(ggplot2)
library(cowplot)
library(lubridate)
library(forcats)
```

## Importing required datasets

You can also embed plots, for example:

```{r}
channels_details <- read.csv("Channel Details.csv")
video_stats <- read.csv("Combined_Dataframe.csv")
```

## Writing a function to represent the scale in thousands, millions and billions for the plots we are going to plot further in this analysis.

```{r}
scale_units <- function(n) {
  labs <- ifelse(n < 1000, n,  # less than thousands
                   ifelse(n < 1e6, paste0(round(n/1e3), 'k'),  # in thousands
                          ifelse(n < 1e9, paste0(round(n/1e6), 'M'),  # in millions
                                 ifelse(n < 1e12, paste0(round(n/1e9), 'B'), # in billions
                                        ifelse(n < 1e15, paste0(round(n/1e12), 'T'), # in trillions
                                               'too big!'
                                        )))))
  return(labs)
}
```

## Plotting various barplots, scatter plots, correlation matrix based on channels_details dataset

### Bar graph representing Comparison of Subscribers of each Channel

```{r}
bar_subs <- ggplot(channels_details, aes(x= Channel_title, y= Subscribers_Count, fill =Channel_title))

bar_subs + geom_bar(stat = "identity")  +
    scale_fill_hue(l=40) +
    scale_y_continuous(labels = scale_units) +
  
  labs(fill = "Channels",
       title = "Comparison of Subscribers of each Channel",
       x = "Channels",
       y = "Subscribers") +
  theme_clean() +
 
  theme(plot.title = element_text(size =14,
                                  face = "bold",
                                  colour = "black",
                                  lineheight = 1.2,
                                  hjust = 0.5
                                  ),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12),
        axis.text.x =   element_text(size = 9),
        axis.text.y = element_text(size = 9),
        legend.title = element_text(size = 14,
                                    face = "bold",
                                    colour = "black")) 
  
```

We can see that Emiway Bantai has highest subscriber count with around 17 million subscribers.
